Pool Model - A unified Mathematical\\ Modeling Framework for Food Science

### 2025-11-06 paper/pool_model.tex
Change order of terms for better comparison of ABM and ODE
Correct mistake in definition of the toxin production (2 type)

\setlength{\tabcolsep}{1.3pt}
\setlength{\columnsep}{0.4cm}
\usepackage{acronym}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{array}
\usepackage{bm}
\usepackage{booktabs}
\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off, font=small]{caption}
\usepackage{diagbox}
\usepackage{float}
\usepackage[T1]{fontenc}
% \usepackage[a4paper,inner=2cm,outer=2cm,top=2.5cm,bottom=2.5cm]{geometry}
\usepackage{graphicx}% Include figure files
\usepackage{here}
\usepackage{hyperref}
\usepackage{lipsum}
\usepackage[switch]{lineno}
\usepackage{mathtools}
\usepackage{mathrsfs}
\usepackage{multirow}
\usepackage{newfloat}
\usepackage{onimage}
\usepackage{siunitx}
\usepackage{subcaption}
\usepackage{tabularx}
\usepackage{tikz}
%\usepackage[dvipsnames]{xcolor}
\usepackage{xpatch}

@@

\title{Pool Model - A unified Mathematical\\ Modeling Framework for Food Science}
\author[1]{Polina Gaindrik}
\author[1]{Jonas Pleyer\fnref{fn1}}
\author[1]{Christian Fleck\corref{cor1}}
\ead{christian.fleck@fdm.uni-freiburg.de}

@@

    \mathcal{F}^2(R,G)&=\kappa\alpha_B R G_B.

@@

        The two species system competing for the common nutrient $R$ with production of the toxin $T_B$ (brown line) calculated using equation~(\ref{eq:model_2sp_toxin}).
        The growing bacteria $B$ produces toxin $T_B$ (A) constantly $\dot{T}_B^1 = \mathcal{F}^1 = \kappa G_B$ or (B) only during growth process $\dot{T}_B^2 = \mathcal{F}^2 = \kappa \alpha_B R G_B$ with
        production rate $\kappa=0.2$.
        The toxin $T_B$ causes the cell death of bacteria $A$ with rate constant $\mu = 0.2$.
        The blue curve describes the growth of the bacteria $B$ ($N_B = L_B+G_B$) with model parameters $\lambda_A=5\cdot 10^{-2}$, $\alpha_A=2.5$.

@@

    \dot{G}_B &= \lambda_B R L_B + \frac{\alpha_B}{1 + \mu_I I} R G_B\\

>>>>

\setlength{\tabcolsep}{1.3pt}
\setlength{\columnsep}{0.4cm}
\usepackage{acronym}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{array}
\usepackage{bm}
\usepackage{booktabs}
\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off, font=small]{caption}
\usepackage{diagbox}
\usepackage{float}
\usepackage[T1]{fontenc}
% \usepackage[a4paper,inner=2cm,outer=2cm,top=2.5cm,bottom=2.5cm]{geometry}
\usepackage{graphicx}% Include figure files
\usepackage{here}
\usepackage{hyperref}
\usepackage{lipsum}
\usepackage[switch]{lineno}
\usepackage{mathtools}
\usepackage{mathrsfs}
\usepackage{multirow}
\usepackage{newfloat}
\usepackage{onimage}
\usepackage{siunitx}
\usepackage{subcaption}
\usepackage{tabularx}
\usepackage{tikz}
%\usepackage[dvipsnames]{xcolor}
\usepackage{xpatch}
\usepackage{orcidlink}

@@

\title{Pool Model - A unified Mathematical\\ Modeling Framework for Food Science}
\author[1]{Polina Gaindrik\orcidlink{0000-0003-0928-3951}}
\author[1]{Jonas Pleyer\fnref{fn1}}
\author[1]{Christian Fleck\corref{cor1}}
\ead{christian.fleck@fdm.uni-freiburg.de}

@@

    \mathcal{F}^2(R,G)&=\kappa R G_B.

@@

        The two species system competing for the common nutrient $R$ with production of the toxin $T_B$ (brown line) calculated using equations~(\ref{eq:model_2sp_toxin}).
        The growing bacteria $B$ produces toxin $T_B$ (A) constantly $\dot{T}_B^1 = \mathcal{F}^1 = \kappa G_B$ or (B) only during growth process $\dot{T}_B^2 = \mathcal{F}^2 = \kappa R G_B$ 
        with production rate $\kappa=0.2~\mathrm{s}^{-1}$.
        The toxin $T_B$ causes the cell death of bacteria $A$ with rate constant $\mu = 0.2~\mathrm{s}^{-1}$.
        The red curve describes the growth of the bacteria $A$ ($N_A = L_A+G_A$) with model parameters $\lambda_A=10^{-2}~\mathrm{s}^{-1}$, $\alpha_A=3.0~\mathrm{s}^{-1}$.
        The blue curve describes the growth of the bacteria $B$ ($N_B = L_B+G_B$) with model parameters $\lambda_B=5\cdot 10^{-2}~\mathrm{s}^{-1}$, $\alpha_B=2.5~\mathrm{s}^{-1}$.

@@

    \dot{G}_A &= \alpha_A R G_A + \lambda_A R L_A\\
    \dot{G}_B &= \frac{\alpha_B}{1 + \mu_I I} R G_B + \lambda_B R L_B\\
    \dot{R} &= -\frac{\alpha_A}{N_t} R G_A-\frac{\alpha_B}{(1 + \mu_I I) N_t} R G_B\\
